---
title: "Real estate analysis"
author: "Jack"
date: "September 17, 2015"
output: 
  slidy_presentation: 
    fig_height: 7.5
    fig_width: 9
---

```{r, echo = F}
source("demo.R")
source("earning.R")
source("earning_all.R")
source("housing.R")

```

```{r, echo = F, variable}
zip <- c(63130, 21231)
zip <- as.character(zip)

```

## Who lives there?
For zip code `r zip`:

```{r, message = F}
graph_demo(zip)

```

## How much do they make (full time)?
For full time employees in zip code `r zip`:
```{r}
earn(zip)

```

## How much do they make (everyone)?
For everyone in zip code `r zip`:
```{r}
earn_all(zip)
```

## Where do they live? Renter vs. owner occupied
For zip code `r zip` the renter vs. owner occupied property:
```{r}
housing(zip)
```

## How many people live in a household?
For zip code `r zip` the renter vs. owner occupied property have typical size of:
```{r}
housing(zip, topic = "household")
```

## How much do they pay for rent?
For zip code `r zip` the typical rent (occupied properties and asking rent):
```{r}
housing(zip, topic = "housing")
```



